testing_summary

### 2024-09-20 data-raw/testing_summary.Rmd
Updated vignettes and saved fitted pk object, changed twofold_test.pk filename and method dispatch documentation.

```{r libraries}
library(devtools)
load_all()
library(magrittr)
```

@@

We have 111 functions and methods in this package! This will be a lot of work to get
through, hence the inspiration for this document. First things first, make a 
"small" version of `cvt` that we can quickly fit. For the purposes of this
document, I will take 5% of CVT_Legacy data.
I will also add a few chemicals + species' data that I know will fail or
be skipped, so that these features may be tested.

```{r tiny-cvt}
tiny_cvt <- cvt %>%
  dplyr::filter(curation_set_tag == "CVT_Legacy") %>%
  dplyr::distinct(analyte_dtxsid, species) %>%
  dplyr::slice_sample(prop = 0.05) %>%
  dplyr::bind_rows(
    data.frame(
      analyte_dtxsid = c("DTXSID00861411", "DTXSID6023577", 
                         "DTXSID1043881", "DTXSID3061635",
                         "DTXSID1021116", "DTXSID2020139"),
      species = rep("rat", 6)
    )) %>%
  dplyr::distinct() %>%
  dplyr::left_join(cvt, by = dplyr::join_by(analyte_dtxsid, species))

@@

```{r minimal-pk}
minimal_pk <- pk(data = tiny_cvt %>%
                   mutate(n_subjects_normalized = if_else(
                     n_subjects_normalized > 1 & is.na(invivPK_conc_sd),
                     min(n_subjects_normalized, 6), n_subjects_normalized)),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = fk_extraction_document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = invivPK_dose_level,
                   Dose.Units = "mg/kg",
                   Subject_ID = fk_subject_id,
                   Series_ID = fk_series_id,
                   Study_ID = fk_study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_normalized,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = invivPK_conc,
                   Value.Units = "mg/L",
                   Value_SD = invivPK_conc_sd,
                   LOQ = invivPK_loq
                 ))

@@

From here I need to set up the pk object settings. I will be using the dose-normalization only,
then re-run using all settings at the end.

```{r pk-settings}
my_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("bobyqa", "L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  stat_error_model(error_group = vars(Chemical, Species, Reference))
```

@@

```{r pre-process}
my_pk <- do_preprocess(my_pk)
my_data <- get_data(my_pk)
# Showing that Chemical + Species + Route + Media + Dose defines
# A CvT experiment, not necessarily Study_ID
my_data %>% dplyr::distinct(Study_ID,
                            Chemical, Species, Route, Media, Dose)

@@

```{r fit}
thispk_profvis <- profvis::profvis(do_fit(my_pk))
system.time(my_pk <- do_fit(my_pk)) # 72 seconds, 11 data_groups

@@

my_rsq <- rsq(my_pk)
```

@@

```{r}
my_AIC <- AIC(my_pk)
my_BIC <- BIC(my_pk)
my_wm <- get_winning_model(my_pk)
```

@@

>>>>

```{r libraries}
library(devtools)
load_all()
library(magrittr)
library(ggplot2)
```

@@

We have 111 functions and methods in this package! This will be a lot of work to get
through, hence the inspiration for this document. First things first, make a 
"small" version of `cvt` that we can quickly fit. For the purposes of this
document, I will take 20% of CVT_Legacy data.
I will also add a few chemicals + species' data that I know will fail or
be skipped, so that these features may be tested.

```{r tiny-cvt}
tiny_cvt <- cvt %>%
  dplyr::filter(curation_set_tag == "CVT_Legacy") %>%
  dplyr::distinct(analyte_dtxsid, species) %>%
  dplyr::slice_sample(prop = 0.20) %>%
  dplyr::bind_rows(
    data.frame(
      analyte_dtxsid = c("DTXSID00861411", "DTXSID6023577", 
                         "DTXSID1043881", "DTXSID3061635",
                         "DTXSID1021116", "DTXSID2020139",
                         "DTXSID3031862"),
      species = rep("rat", 7)
    )) %>%
  dplyr::distinct() %>%
  dplyr::left_join(cvt, by = dplyr::join_by(analyte_dtxsid, species))

@@

```{r minimal-pk}
flat_chems <- paste0("DTXSID",
                     c(2020139,
                       5037523,
                       8020541,
                       8025337,
                       5034773,
                       4021268))

minimal_pk <- pk(data = cvt %>%
                   # filter(analyte_dtxsid %in% flat_chems) %>%
                   mutate(n_subjects_normalized = if_else(
                     n_subjects_normalized > 1 & is.na(invivPK_conc_sd),
                     min(n_subjects_normalized, 6), n_subjects_normalized)),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = fk_extraction_document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = invivPK_dose_level,
                   Dose.Units = "mg/kg",
                   Subject_ID = fk_subject_id,
                   Series_ID = fk_series_id,
                   Study_ID = fk_study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_normalized,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = invivPK_conc,
                   Value.Units = "mg/L",
                   Value_SD = invivPK_conc_sd,
                   LOQ = invivPK_loq
                 ))

@@

From here I need to set up the pk object settings.
I will be using all settings as TRUE.

```{r pk-settings}
my_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c(
    "bobyqa",
    "L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  scale_time(new_units = "auto") +
  stat_error_model(error_group = vars(Chemical, Species, Reference))
```

@@

```{r pre-process}
my_pk <- do_preprocess(my_pk)
my_data <- get_data(my_pk)
my_data %>% dplyr::distinct(Chemical, Species) %>% NROW()
```

@@

```{r fit}
thispk_profvis <- profvis::profvis(do_fit(my_pk))
system.time(my_pk <- do_fit(my_pk))
system.time(my_pk <- do_fit(my_pk, n_cores = 10))
my_pk <- do_fit(my_pk)
# 100 seconds, 11 data_groups
# 270 seconds, 25 data_groups
# 12 cores, full dataset:  489 seconds

get_winning_model(my_pk) %>% View()
```

@@

my_rsq <- rsq(my_pk)

plot(my_rsq$Rsq, my_rmsle$RMSLE)
```

@@

```{r}
my_AIC <- AIC(my_pk)
my_BIC <- BIC(my_pk)
my_wm <- get_winning_model(my_pk)
table(my_wm$model)

@@

Plotting is of the important outputs of _invivoPKfit_, as it allows
people to visualize the predictions and form a second opinion on the
fits.

```{r}
mypl <- plot(my_pk, best_fit = TRUE)
```
